Multiple imputation of incomplete multilevel data using Heckman selection models

### 2022-11-10 1.Paper/Paper.Rmd
Update cache

#### Continuous incomplete variable
 ```{r rhocont,fig.pos="!htb",fig.cap="\\label{fig:rhocont} Continuous incomplete variable by varing $\\rho$, the dashed line depicts the target performance criteria value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_rho
 ```

@@

 ```{r rhobin,fig.pos="!htb",fig.cap="\\label{fig:bin} Binary incomplete variable by varing $\\rho$, the dashed line depicts the target performance criteria value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_bin
```

@@

```{r size,fig.pos="h",fig.cap="\\label{fig:size} Continuous incomplete variable under systematical missingness by varing: number of clusters (N); sample size per cluster ($n_i$), the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_N
```

@@

```{r dist,fig.pos="!H",fig.cap="\\label{fig:dist} Comparison of methods for continuous incomplete variable with deviations in distribution assumptions, where the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_S
```
<!-- Ideally, the phrase " where the dashed line depicts the true simulated parameter" belongs in a note under the caption. -->

@@

# An illustrative study
\label{example}
```{r, include=FALSE}
library(here)
# source(here('3.Ilustrative_study','Ilustrative_study.R'),local = knitr::knit_global())
```

@@

```{r descriptive, results = "asis", table.pos="!H", echo=FALSE}
# if (!require("xtable")) install.packages("xtable")
# xt <- xtable(sum.table,
#              caption = "Descriptive analysis, predictor variables", label = "tab:descriptive",align= c("p{0.0\\textwidth}|",
#                                    "p{0.11\\textwidth}|",
#                                    "p{0.07\\textwidth}|",
#                                    "p{0.07\\textwidth}|",
#                                    "p{0.05\\textwidth}|",
#                                    "p{0.10\\textwidth}|",
#                                    "p{0.12\\textwidth}|",
#                                    "p{0.07\\textwidth}|",
#                                    "p{0.07\\textwidth}|",
#                                    "p{0.07\\textwidth}|",
#                                    "p{0.07\\textwidth}|"))
# names(xt) <- c("Subregion","Districts (N)","Children (N)","Age mean (years)",
#                 "Log10 Female Anopheline","Wealth index",
#                 "Bednet (%)","Females (%)","Holidays (%)",
#                 "Missing test(%)")
# print(xt, comment = FALSE, include.rownames=FALSE)
```

@@

```{r ERV, results = "asis", table.pos="!H", echo=FALSE}
# if (!require("xtable")) install.packages("xtable")
# xt <- xtable(tablexc,
#              caption = "Evaluation of Holidays as exclusion restriction variable", label = "tab:exclusion")
# names(xt) <- c("","Test result (y)"," Missing indicator (ry)")
# comment<- list( pos=list(0),command=NULL)
# comment$pos[[1]]<-c(nrow(xt))
# comment$command<-c(paste("\\hline",
#                          "***p<0.01",sep=" "))
# 
# print(xt, comment = FALSE, include.rownames=FALSE,add.to.row = comment,
#       hline.after = c(-1,0))
```
<!-- What are non-participants? Children with missing values? -->
According to our imputation approach, non-participants were estimated to have a higher prevalence of malaria than participants in more than half of the districts analyzed. 
As can be seen in Figure \ref{fig:region}, for each subregion the prevalence estimates of the approaches do not differ significantly between methods. However, prevalence estimates under the MNAR assumption (i.e. 2 level Heckman)  are higher than those estimated under the MAR or MCAR aproaches, except for the East-Central region. 
```{r region,fig.width = 5, fig.asp =.67, fig.pos="!H", fig.cap="\\label{fig:region} Estimates of malaria prevalence by Uganda subregion",echo=FALSE,fig.keep="last"}
# plot_dist
```

@@

```{r region_age, fig.pos="!H", fig.cap="\\label{fig:region_age} Estimation of malaria prevalence by region and age",echo=FALSE,fig.keep="last"}
# plot_sdist_age
```

@@

### Conclusion
<!-- Always add a conclusion, also in stats papers. I'm thinking it should mention the following. I am not so sure on especially the last sentence, so feel free to rephrase -->
We have <!--(well actually you) --> proposed an extension to the Heckman model that can account for MNAR, MAR or MCAR of a continuous or binary variable in clustered data sets. Our simulations showed that it has favorable statistical properties, when assumptions were met, and provided that the sample size was sufficiently large. Regarding deviations from distributional assumptions of the error terms, the coefficient parameters were fairly robust in terms of bias, but the intercept was not.

>>>>

#### Continuous incomplete variable
 ```{r rhocont,fig.align='center',fig.pos="!htb",fig.cap="\\label{fig:rhocont} Continuous incomplete variable by varing $\\rho$, the dashed line depicts the target performance criteria value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_rho
 ```

@@

 ```{r rhobin,fig.align='center',fig.pos="!htb",fig.cap="\\label{fig:bin} Binary incomplete variable by varing $\\rho$, the dashed line depicts the target performance criteria value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_bin
```

@@

```{r size,fig.align='center',fig.pos="!htb",fig.cap="\\label{fig:size} Continuous incomplete variable under systematical missingness by varing: number of clusters (N); sample size per cluster ($n_i$), the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_N
```

@@

```{r dist,fig.align='center',fig.pos="!htb",fig.cap="\\label{fig:dist} Comparison of methods for continuous incomplete variable with deviations in distribution assumptions, where the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last",fig.height = 4, fig.width = 6}
plot_S
```
<!-- Ideally, the phrase " where the dashed line depicts the true simulated parameter" belongs in a note under the caption. -->

@@

# An illustrative study
\label{example}
```{r, include=FALSE,cache = TRUE}
library(here)
 source(here('3.Ilustrative_study','Ilustrative_study.R'),local = knitr::knit_global())
```

@@

```{r descriptive,fig.align='center',cache = TRUE, results = "asis", table.pos="!htb", echo=FALSE}
if (!require("xtable")) install.packages("xtable")
xt <- xtable(sum.table,
             caption = "Descriptive analysis, predictor variables", label = "tab:descriptive",align= c("p{0.0\\textwidth}|",
                                   "p{0.11\\textwidth}|",
                                   "p{0.07\\textwidth}|",
                                   "p{0.07\\textwidth}|",
                                   "p{0.05\\textwidth}|",
                                   "p{0.10\\textwidth}|",
                                   "p{0.12\\textwidth}|",
                                   "p{0.07\\textwidth}|",
                                   "p{0.07\\textwidth}|",
                                   "p{0.07\\textwidth}|",
                                   "p{0.07\\textwidth}|"))
names(xt) <- c("Subregion","Districts (N)","Children (N)","Age mean (years)",
                "Log10 Female Anopheline","Wealth index",
                "Bednet (%)","Females (%)","Holidays (%)",
                "Missing test(%)")
print(xt, comment = FALSE, include.rownames=FALSE)
```

@@

```{r ERV,fig.align='center', cache = TRUE,results = "asis", table.pos="!htb", echo=FALSE}
if (!require("xtable")) install.packages("xtable")
xt <- xtable(tablexc,
             caption = "Evaluation of Holidays as exclusion restriction variable", label = "tab:exclusion")
names(xt) <- c("","Test result (y)"," Missing indicator (ry)")
comment<- list( pos=list(0),command=NULL)
comment$pos[[1]]<-c(nrow(xt))
comment$command<-c(paste("\\hline",
                         "***p<0.01",sep=" "))

print(xt, comment = FALSE, include.rownames=FALSE,add.to.row = comment,
      hline.after = c(-1,0))
```
<!-- What are non-participants? Children with missing values? -->
According to our imputation approach, non-participants were estimated to have a higher prevalence of malaria than participants in more than half of the districts analyzed. 
As can be seen in Figure \ref{fig:region}, for each subregion the prevalence estimates of the approaches do not differ significantly between methods. However, prevalence estimates under the MNAR assumption (i.e. 2 level Heckman)  are higher than those estimated under the MAR or MCAR aproaches, except for the East-Central region. 
```{r region,fig.align='center',fig.width = 5, fig.asp =.67, fig.pos="!htb", fig.cap="\\label{fig:region} Estimates of malaria prevalence by Uganda subregion",echo=FALSE,fig.keep="last",cache = TRUE}
 plot_dist
```

@@

```{r region_age,fig.align='center', fig.pos="!htb", fig.cap="\\label{fig:region_age} Estimation of malaria prevalence by region and age",echo=FALSE,fig.keep="last",cache = TRUE}
plot_sdist_age
```

@@

## Conclusion
<!-- Always add a conclusion, also in stats papers. I'm thinking it should mention the following. I am not so sure on especially the last sentence, so feel free to rephrase -->
We have <!--(well actually you) --> proposed an extension to the Heckman model that can account for MNAR, MAR or MCAR of a continuous or binary variable in clustered data sets. Our simulations showed that it has favorable statistical properties, when assumptions were met, and provided that the sample size was sufficiently large. Regarding deviations from distributional assumptions of the error terms, the coefficient parameters were fairly robust in terms of bias, but the intercept was not.
